[![Build Status](https://travis-ci.org/mpadge/tnorm?branch=master)](https://travis-ci.org/mpadge/tnorm)
[![codecov](https://codecov.io/gh/mpadge/tnorm/branch/master/graph/badge.svg)](https://codecov.io/gh/mpadge/tnorm)

# tnorm

This package exists merely as a faster replacement for the core functionality of
other packages. It generates vectors of random values from a truncated normal
distribution. This functionality already exists in both

1. [msm::rtnorm](https://cran.r-project.org/package=msm), which is entirely
   R-based, and

2. [truncnorm::rtruncnorm](https://cran.r-project.org/package=truncnorm), which
   has core code in C.

Even the latter of these is, however, slower than `tnorm` at generating random
values. `tnorm` currently generates distributions centred around a mean value of
1, truncated to between 0 and 2. Values can be readily re-scaled to desired mean
values and limits.


--------


## Install

```{r, eval=FALSE}
devtools::install_github ('mpadge/tnorm')
```
```{r load, echo=FALSE, message=FALSE}
while (length (grep ('tnorm', getwd ())) > 0) setwd ("..")
#devtools::document ("tnorm")
#devtools::check ("tnorm")
#Rcpp::compileAttributes ("tnorm")
devtools::load_all ("tnorm")
setwd ("./tnorm")
#testthat::test_package ('tnorm')
```

-----

## Use

The one and only function
```{r}
z <- tnormn (n=1e5, sd=1)
```

## Compare timing with `msm::rtnorm` and `truncnorm::rtruncnorm`


```{r}
fns <- c ('tnormn', 
          get ('rtnorm', asNamespace ('msm'), mode='function'),
          get ('rtruncnorm', asNamespace ('truncnorm'), mode='function'))
n <- 1e5
mn <- sd <- 1
args <- list (list (n=n, sd=sd), 
              list (n=n, mean=mn, sd=sd, lower=0, upper=2),
              list (n=n, mean=mn, sd=sd, a=0, b=2))
st <- sapply (1:3, function (i) {
                  set.seed (1)
                  system.time (do.call (fns [[i]], args [[i]]))[1]
              })
st
```
And the speed-ups are
```{r}
as.numeric (st [2] / st [1]); as.numeric (st [3] / st [1])
```
And `tnormn` is still several times faster than `rtruncnorm`.
